Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-03-16 supp/supp.qmd
Adding table for countries and a bit of writing

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer)

@@

Unsurprisingly, countries in North America and Europe use preprints more exstensively compared to other countries with countries in Africa, Central America and parts of Asia still slow to use *EcoEvoRxiv* for their preprints (@fig-countries).

@@

# List unique countries
  maps_country_name <- unique(world_map$region) # Names of regions in maps
  countries[!countries$country %in% maps_country_name,] # Names of countries in our data that are not in the maps data, we need to fix these in countries

@@

@@

>>>>

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable)

@@

@@

# List unique countries
  maps_country_name <- unique(world_map$region) # Names of regions in maps
  #countries[!countries$country %in% maps_country_name,] # Names of countries in our data that are not in the maps data, we need to fix these in countries

@@

# Find the countries with 90% of the preprints

most_use <- countries[cumsum(countries$valid_percent) <= 0.90, ]

@@

A total of `r length(unique(countries$country))-1` countries have used *EcoEvoRxiv* as a preprint server. Unsurprisingly, countries in North America and Europe use preprints more exstensively. Countries in Africa, Central America and parts of Asia are still slow to use *EcoEvoRxiv* for their preprints (@fig-countries). Overall, 90% of the preprints come from `r nrow(most_use)-1` countries (@tbl-countries).

```{r}
#| label: tbl-countries
#| tbl-cap: Countries with 90% of the preprints on EcoEvoRxiv.

tbl_most <- most_use %>% filter(!is.na(valid_percent)) %>% mutate(Percentage = valid_percent*100) %>% select(country, Percentage)  %>% rename("Country" = country)

flextable(tbl_most) %>% bold(part = "header") %>% autofit()
```
